\textls[-0]{\thetitle}

### 2023-03-31 body.tex
Start working on appendices.
Save Canonicity Model.
ack Zhixuan
tweaks
Set out the frame

\begin{abstract}
\input{abstract}
\end{abstract}

\maketitle

@@

\section{\TT: A Core Dependent Type Theory}
\label{sec:metatheory2}
\input{metatheory-condensed.tex}

@@

\ifacknowledgments
\section*{Acknowledgments}
We thank the reviewers for their many useful comments.  We thank
Anastasiya Kravchuk-Kirilyuk, Yao Li, and Andrew Myers % others?
for valuable discussions.
This work was supported in part by an Amazon research award on automated
reasoning.
The views and opinions expressed are those of the authors and do not necessarily
reflect the position of any funding agency.
\fi

@@

\ifreport

\appendix

@@

\section{More Typing Rules for \TT}
\label{sec:more-rules}
\input{all-typing-rule.tex}

@@

\section{Definitive Version of the Formalization and Proofs}
\label{sec:agda-files}
\input{agda-files.tex}

@@

\fi

>>>>

% \begin{abstract}
% \input{abstract}
% \end{abstract}

% \maketitle

\section*{Family Polymorphism by Coq Plugin}

@@

\section{A Preview of \TT: A Core Dependent Type Theory}
\label{sec:metatheory2}
\input{metatheory-condensed.tex}

@@

\ifacknowledgments
\section*{Acknowledgments}
We thank the reviewers for their many useful comments.  We thank
Anastasiya Kravchuk-Kirilyuk, Yao Li, Andrew Myers, and Zhixuan Yang
for valuable discussions and feedback.
This work was supported in part by an Amazon research award on automated
reasoning.
The views and opinions expressed are those of the authors and do not necessarily
reflect the position of any funding agency.
\fi

@@

% \ifreport

% \appendix

@@

\section*{Technicality of \TT}

\section{Syntax and Semantic Models of \TT}
\label{sec:complete-fmltt}
% \input{all-typing-rule.tex} -- we make all-typing rules into metatheory2.tex
\input{metatheory2.tex}

@@

% \newpage

% \section{Definitive Version of the Formalization and Proofs}
% \label{sec:agda-files}
% \input{agda-files.tex}

@@

% \fi
